\documentclass{resume}

\usepackage[T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{microtype}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\hypersetup{colorlinks=true, urlcolor=cyan}

\hyphenpenalty=1

\name{Tamika Nomara}

\address{(she/her or they/them)}
\address{
    \href{mailto:taminomara@gmail.com}{taminomara@gmail.com}
    \\
    \url{https://github.com/taminomara}
}

\begin{document}

    Senior Rust/C++ developer with passion for distributed systems.
    
    I love seeing results of my work making the world a better place.
    
    I believe that a diverse team and good working environment
    is a requirement for creating great things.
    
    Untested code cannot be trusted, undocumented APIs might
    as well not exist.

    \begin{rSection}{Skills}
        \begin{rSubsection}{}{}{}{}
            \item
                Rust;
                C++ 17/20;
                Python 3.
                CI, CD, TDD, Version control.
            \item
                Distributed, scalable high-load systems;
                Compilers;
                Developer productivity
                (infrastructure, tooling, etc).
        \end{rSubsection}
        \begin{rSubsection}{}{}{}{}
            \item
                Building software with reliability and ergonomics in mind.
            \item
                Designing type-safe APIs that are easy and intuitive to use.
        \end{rSubsection}
        \begin{rSubsection}{}{}{}{}
            \item
                Owning systems,
                being responsible for their architecture, development and operations.
            \item
                Proposing, designing and implementing new ideas,
                being pro-active.
            \item
                Ensuring that my solutions are
                effective, clean, well tested and documented.
            \item
                Working in a team,
                collaborating with other teams,
                mentoring junior colleagues.
        \end{rSubsection}
    \end{rSection}

    \begin{rSection}{Experience}
        \begin{rSubsection}{Gnosis LLC}{May 2021~--~February 2022}{Senior software engineer}{}
            \item
                Used Rust to build and improve
                a distributed cryptocurrency exchange (Gnosis Protocol),
                as well as the infrastructure around the project.
            \item
                Refactored the way we report Prometheus metrics
                by introducing a new library
                \href{https://github.com/taminomara/prometheus-metric-storage}{prometheus-metric-storage}.
                It turned adding and maintaining metrics into an easy task,
                improving observability of the service.
            \item
                Implemented a system for
                \href{https://docs.rs/ethcontract-mock/latest/ethcontract_mock/}{mocking Ethereum contracts}
                without having to run a blockchain instance.
                It has greatly improved testability of the codebase.
            \item
                Used python to automate several on-call processes,
                making it easier to deploy services and keep them healthy.
                By-product of this task is a small CLI library called
                \href{https://github.com/taminomara/yuio}{Yuio}.
        \end{rSubsection}

        \begin{rSubsection}{Yandex N.V.}{July 2016~--~December 2020}{Software engineer}{}
            \item
                Designed and implemented an in-memory database
                for our monitoring service.
                Fault-tolerant, horizontally scalable,
                it uses async C++ to provide on-line access
                to the health status of thousands of systems.
            \item
                Developed an LLVM-powered C++ library
                for extracting data from logs.
                It uses map-reduce to handle hundreds of TBs of logs daily;
                it has increased parsing speed
                by 30\% and improved quality of analytics.
            \item
                Developed an efficient Python framework
                for calculating results of AB experiments using map-reduce.
                It has reduced the barrier
                to integrate AB testing into a service,
                enabling more Yandex projects to use AB\@.
        \end{rSubsection}
    \end{rSection}

    \begin{rSection}{Education}
        \begin{rSubsection}{Bachelor of Computer Science}{2014~--~2018}
        {National Research University Higher School of Economics, Moscow, Russia}{}
            Major in Distributed Computing
        \end{rSubsection}
    \end{rSection}

\end{document}
